% =============================================================================
% Jose Carlos Chaparro, Full Stack Engineer CV
% Single-column ATS-friendly layout
% Compile with: pdflatex cv_chaparro.tex
% =============================================================================

\documentclass[10pt,letterpaper]{article}

% ----- Packages -----
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[top=0.5in,bottom=0.5in,left=0.65in,right=0.65in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage[default]{lato}
\renewcommand*\familydefault{\sfdefault}

% ----- Colors -----
\definecolor{accent}{HTML}{1F3A5F}     % dark navy
\definecolor{subtle}{HTML}{555555}
\definecolor{rule}{HTML}{C0C0C0}

% ----- Hyperlink style -----
\hypersetup{
    colorlinks=true,
    urlcolor=accent,
    linkcolor=accent,
    pdftitle={Jose Chaparro - Full Stack Engineer CV},
    pdfauthor={Jose Carlos Chaparro Morales}
}

% ----- Section style -----
\titleformat{\section}
    {\large\bfseries\color{accent}}
    {}{0pt}
    {}[\vspace{-5pt}\color{rule}\hrule height 0.5pt\vspace{3pt}]
\titlespacing*{\section}{0pt}{4pt}{1pt}

\titleformat{\subsection}
    {\normalsize\bfseries}
    {}{0pt}{}
\titlespacing*{\subsection}{0pt}{6pt}{1pt}

% ----- List style (compact) -----
\setlist[itemize]{leftmargin=11pt, itemsep=0pt, topsep=0pt, parsep=0pt}

% ----- Helper commands -----
\newcommand{\role}[4]{%
    \noindent\textbf{#1} \hfill \textcolor{subtle}{#3}\\
    \textit{#2} \hfill \textcolor{subtle}{\textit{#4}}\par\vspace{1pt}
}

\newcommand{\skillcat}[2]{\noindent\textbf{#1:} #2\par\vspace{1pt}}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}

% =============================================================================
\begin{document}
% =============================================================================

% ----- Header (ATS-friendly: plain text, no glyphs) -----
\begin{center}
    {\Huge\bfseries\color{accent} José Carlos Chaparro}\\[1pt]
    {\large Full Stack Engineer}\\[4pt]
    \small
    +52 614 215 2635 | \href{mailto:jc_chaparro@hotmail.com}{jc\_chaparro@hotmail.com} | \href{https://www.linkedin.com/in/jose-c-chaparro/}{linkedin.com/in/jose-c-chaparro} | \href{https://github.com/JoseCarlosChaparro}{github.com/JoseCarlosChaparro} | \href{https://www.josechaparro.com}{www.josechaparro.com}\\[1pt]
    Mexico-based $\cdot$ Open to remote / US relocation $\cdot$ \textbf{US Citizen (no sponsorship required)}\\[1pt]
    Languages: Spanish (native) $\cdot$ English (professional working proficiency)
\end{center}

% ----- Professional Profile -----
\section*{Professional Profile}
Full Stack Engineer with 2+ years of production experience building backend systems in Python (FastAPI) and C\# (.NET) on AWS and Linux. Shipped a containerized ML platform from scratch; previously maintained an ERP serving 170+ branches and 1,750+ employees. Owns the full SDLC: requirements, coding, QA, deployment, and production support.

% ----- Technical Skills -----
\section*{Technical Skills}
\skillcat{Languages}{Python, JavaScript, TypeScript, C\#, SQL}
\skillcat{Backend}{FastAPI, Django, Node.js, .NET Framework}
\skillcat{Frontend}{React, React Native, Next.js}
\skillcat{Databases}{PostgreSQL, SQL Server}
\skillcat{Cloud \& DevOps}{AWS (EC2, RDS, S3, IAM, Secrets Manager), Docker, Docker Compose, Nginx, Cloudflare, Dokploy, Git, GitHub Actions, Linux}

% ----- Work Experience -----
\section*{Work Experience}

\role{Full Stack Engineer}{Moneta Market}{August 2025 -- Present}{}
\begin{itemize}
    \item Architected the company's first containerized platform on AWS EC2 (Linux): 6-service Docker Compose stack (2 FastAPI microservices, Label Studio, MLflow, Nginx reverse proxy) replacing manual deployment with reproducible automation.
    \item Designed an 18-table PostgreSQL schema on AWS RDS (18 foreign keys, 28+ indexes, idempotent migrations, soft-delete audit trail) accessed via SSH tunnel through EC2 bastion host.
    \item Built an event-driven FastAPI webhook integrating Label Studio with S3: Repository pattern, atomic DB/S3 rollback, async connection pooling, in-memory cache with DB fallback; wrote runbooks for team onboarding.
    \item Developed a cross-platform C\# desktop app (.NET 10, Avalonia, migrated from WPF) for ML-frame human review: MVVM, two-pass verification, sliding-window prefetch cache.
    \item Set up least-privilege IAM, AWS Secrets Manager, LocalStack for local S3, and GitHub Actions CI; co-supervise 2 interns with the lead developer.
\end{itemize}

\role{Freelance Full Stack Engineer (Part-time)}{Independent Contractor}{February 2025 -- Present}{concurrent with Moneta Market role}
\begin{itemize}
    \item Deliver full-stack web and mobile apps end-to-end (React, React Native, Next.js, FastAPI, Django) on PostgreSQL. Self-host on a personal Linux server using Dokploy, Docker Compose, and Cloudflare Tunnels, a low-cost alternative to Vercel/AWS for clients.
\end{itemize}

\role{.NET Software Developer}{Grupo Roga}{March 2024 -- August 2025}{}
\begin{itemize}
    \item Maintained and extended a mission-critical ERP serving 170+ branches and 1,750+ employees (Mueblería El Pasito / Villarreal Muebles / Dinexpress); built multi-branch inventory, pricing, accounts receivable, and POS modules in .NET Framework on Windows.
    \item Designed SQL Server architecture for multi-branch retail: stored procedures for inventory aggregation and pricing, automated reporting via SQL Server Agent jobs, eliminating manual report compilation for operations.
\end{itemize}

% ----- Education -----
\section*{Education}

\noindent\textbf{Bachelor of Science in Computer Science Engineering}, Universidad Autónoma de Chihuahua \hfill \textcolor{subtle}{2018 -- 2023}\\
GPA 9.2 / 10, graduated by academic merit.

\end{document}
